Ecosystem functional response across precipitation extremes in a sagebrush steppe

### 2017-11-13 manuscript/usses_water_ms.Rmd
adds new opening paragraph

\new{Water availability is a major driver of annual net primary productivity (ANPP) in grassland ecosystems} [@Huxman2004; @Hsu2012].
\new{}

>>>>

\new{Water availability is a major driver of annual net primary productivity (ANPP) in grassland ecosystems} [@Huxman2004; @Hsu2012].
\new{Therefore, projected changes in precipitation regimes, associated with global climate change, will impact grassland ecosystem functioning.
Increases in precipitation variability will result in prolonged periods of extremely wet or dry years, and predicting the consequences of such chronic resource alterations requires understanding how ecosystems respond to above and below average precipitation levels.}

### 2017-11-13 manuscript/usses_water_ms.tex
adds new opening paragraph

At any given site, the relationship between aboveground net primary
productivity (ANPP) and water availability (e.g., soil moisture) can be
characterized by regressing historical observations of ANPP on
observations of soil moisture. Fitted functional responses can then be
used to infer how ANPP may change under future precipitation regimes
\citep[e.g.,][]{Hsu2012}. A problem with this approach is that it
requires extrapolation if future precipitation falls outside the
historical range of variability \citep{Smith2011, Peters2012}. For
example, the soil moisture-ANPP relationship may be linear within the
historical range of interannual variation, but could saturate at higher
levels of soil moisture. In fact, saturating relationships are actually
common \citep{Hsu2012, Gherardi2015a}, perhaps because other resources,
like nitrogen, become more limiting in wet years than dry years. Failure
to accurately estimate the curvature of the soil moisture-ANPP
relationship will lead to over- or underprediction of ANNP under extreme
precipitation \citep{Peters2012}.

>>>>

\new{Water availability is a major driver of annual net primary productivity (ANPP) in grassland ecosystems}
\citep{Huxman2004, Hsu2012}.
\new{Therefore, projected changes in precipitation regimes, associated with global climate change, will impact grassland ecosystem functioning.
Increases in precipitation variability will result in prolonged periods of extremely wet or dry years, and predicting the consequences of such chronic resource alterations requires understanding how ecosystems respond to above and below average precipitation levels.}

At any given site, the relationship between ANPP and water availability
(e.g., soil moisture) can be characterized by regressing historical
observations of ANPP on observations of soil moisture. Fitted functional
responses can then be used to infer how ANPP may change under future
precipitation regimes \citep[e.g.,][]{Hsu2012}. A problem with this
approach is that it requires extrapolation if future precipitation falls
outside the historical range of variability
\citep{Smith2011, Peters2012}. For example, the soil moisture-ANPP
relationship may be linear within the historical range of interannual
variation, but could saturate at higher levels of soil moisture. In
fact, saturating relationships are actually common
\citep{Hsu2012, Gherardi2015a}, perhaps because other resources, like
nitrogen, become more limiting in wet years than dry years. Failure to
accurately estimate the curvature of the soil moisture-ANPP relationship
will lead to over- or underprediction of ANNP under extreme
precipitation \citep{Peters2012}.
